Reduced plasticity and opportunity for selection in terrestrial ectotherm populations

### 2023-04-15 ms.qmd
Adding in start to making predcitions. Each habitat will need it's own so will subset data. Then, need to ake sure unique . distinct lata nd longs are in new data.

>>>>

# Now we need to make predictions for new data. We first need to create new data. We need to do this for each habitat type because they are all a little different. Lets do terrestrial first.
  terrest_data <- sub_data  %>% filter(habitat == "t")
    new_data_t <- data.frame(
      spp = terrest_data$spp,
      trait = terrest_data$trait,
      habitat = terrest_data$habitat,
      c_accl_time = 0,
      V = 0,
      effect_size = 0,
      lat = terrest_data$lat.y,
      long = terrest_data$long.x
    )

terre_pred <- predict(model5_bayes, newdata = new_data_t, summary = FALSE)
